\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubItemListStart}{\begin{itemize}[leftmargin=*]\vspace{-5pt}}
\newcommand{\resumeSubItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://yangtaoge518.github.io/JardinDesCodes/}{\Large Yangtao Ge}} & Email : \href{mailto:yangtao.ge@outlook.com}{yangtao.ge@outook.com}\\
  \href{https://www.linkedin.com/in/yangtaoge/}{https://www.linkedin.com/in/yangtaoge/} & Mobile : +44-7410369839 \\
   &Github: \href{https://github.com/YangtaoGe518}{YangtaoGe518}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University College London}{London, UK}
      {Master of Engineering (MEng) in Computer Science;   Degree Award: First Class Honours}{Sept. 2018 -- Sept. 2022}
    \resumeSubheading
      {University College London}{London, UK}
      {Undergraduate Preparatory Certificate;  Avg. Score 86/100}{Sept. 2017 -- June. 2018}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Professional Summary}
Accomplished Backend Software Engineer with two years of full-time experience at Smartsheet, enhanced by internships at Spotify and R3. Specializes in building and managing microservices on AWS platforms like EKS and ECS, and proficient in developing robust CI/CD pipelines and infrastructure solutions with Terraform. Currently a Software Engineer II, I manage and own key services from inception to deployment, collaborating effectively with cross-functional teams. Committed to broadening my software engineering expertise while deepening my specialization in cloud infrastructure and security, I am actively developing into a T-shaped professional with comprehensive knowledge and deep technical skills


%--------PROGRAMMING SKILLS------------
\section{Personal Skills}
    \resumeItemListStart
        \resumeItem{Programming Languages}{
          \resumeSubItemListStart
            \resumeSubItem{Java}{Proficient in building scalable server-side applications using Spring Framework and Gradle.}
            \resumeSubItem{Golang}{Proficient in building concurrent applications, primarily for microservices using Chi and Gin frameworks.}
            \resumeSubItem{Python}{Skilled in scripting and automation, as well as backend development with AWS Lambda.}
            \resumeSubItem{Other Languages}{C/C++ (Competent); JavaScript (Proficient); SQL (Proficient)}
          \resumeSubItemListEnd
        }
        \resumeItem{Cloud Platform \& Tools}{
          \resumeSubItemListStart
            \resumeSubItem{AWS}{Experienced with EC2, SQS, S3, and Lambda for cloud-based applications building with \texttt{terraform}}
            \resumeSubItem{Docker}{Strong capabilities in containerization and version control of deployment environments.}
            \resumeSubItem{Kubernetes \& ECS}{Proficient in orchestrating and managing containerized applications in AWS EKS and ECS}
          \resumeSubItemListEnd
        }
        \resumeItem{DevOp \& Analytic}{
          \resumeSubItemListStart
            \resumeSubItem{GitLab/GitHub}{Proficient with git for version control and building CI/CD pipelines.}
            \resumeSubItem{OpenSearch}{Implemented for search and log analysis solutions using Fluentd in containerized environments.}
            \resumeSubItem{Datadog \& Grafana}{Proficient in building interactive dashboards for real-time data visualization and analytics.}
          \resumeSubItemListEnd
        }
    \resumeItemListEnd
    
%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
  {Smartsheet}{London, UK}
  {Software Engineer II}{Jan. 2023 - Present}
  \resumeItemListStart
    \resumeItem{Golang Microservices}
      {Developed backend API services using the Golang CHI framework to facilitate access to cell history data from an S3 bucket. Optimized data retrieval processes by implementing parallel fetches with goroutines, enhancing performance by 20\% on P95 latency measures.}
    \resumeItem{Analytic Tool Integration}
      {Integrated FluentD as a log layer to streamline the delivery of application logs to OpenSearch via AWS Kinesis Stream. Developed and implemented a Datadog dashboard for real-time data visualization, significantly enhancing incident response times by enabling quicker issue identification.}
    \resumeItem{GitLab CI/CD Pipeline}
      {Implemented deployment pipelines using GitLab Runner for automated validation and promotion of container images. This initiative accelerated the team's development cycle by 50\%, improving deployment efficiency on AWS ECS clusters.}
  \resumeItemListEnd
  \resumeSubheading
  {Spotify}{London, UK}
  {Backend Engineer Intern}{June. 2022 - Sept. 2022}
  \resumeItemListStart
    \resumeItem{Java Microservices}
      {Developed backend microservices using the Apollo framework and gRPC, which enhances music delivery processes and service efficiency for both music providers and Spotify operatives.}
    \resumeItem{Testing Enhancement}
      {Authored technical documentation outlining key strategies for testing improvements, which was instrumental in increasing code coverage from 75\% to 90\%, substantially boosting application reliability}
    \resumeItem{Operational Integration}
      {Engineered a Slack notification workflow that automatically informs Spotify operatives of stakeholder status updates, enhancing operational communication and responsiveness.}
  \resumeItemListEnd


  %-----------EXPERIENCE: R3 (Blockchain & Finance)-----------------
  \resumeSubheading
  {R3}{London, UK}
  {Solution Engineer}{June. 2021 - Sept. 2021}
  \resumeItemListStart
    \resumeItem{Confidential Computing Development}
      {Actively contributed to the enhancement of the Conclave example codebase utilizing Kotlin and Java, which has been utilized in commercial sales processes, demonstrating practical applications of confidential computing in business solutions.}
    \resumeItem{Corda Certification}
      {Successfully passed Corda Developer Certification Exam, validating expertise in enterprise blockchain technology such as distributed ledger and contracts. \href{https://www.credly.com/badges/43679dc7-46c4-4fe1-a4bf-a5f173e026d2}{[Credly Credential]}}
  \resumeItemListEnd

  %-----------EXPERIENCE: Healios (React Native)-----------------
  \resumeSubheading
  {Healios}{London, UK}
  {React Native Developer}{Dec. 2020 - Jun. 2021}
  \resumeItemListStart
    \resumeItem{React Native Development}
      {Participated in the development of "ThinkNinja," an NHS-affiliated app designed to educate children about mental health, utilizing React Native and TypeScript. Successfully implemented multi-language support, which enhancing user accessibility and engagement.}
    \resumeItem{Code Quality and Efficiency}
      {Improved code robustness and maintainability by integrating TypeScript and ESLint. Optimized development workflows by configuring Redux for state management and Redux-Saga for handling asynchronous operations, thereby boosting overall code efficiency.}
    \resumeItem{Continuous Integration and Testing}
      {Integrated TestFairy to streamline internal app distributions. Developed and implemented a continuous integration pipeline that reduced deployment cycles by 30\%, substantially enhancing team productivity and application reliability.}
  \resumeItemListEnd


%-----------EXPERIENCE: EMIS (Backend & Data)-----------------
  \resumeSubheading
  {EMIS Health Group}{London, UK}
  {Software Engineer Intern}{Jun. 2020 - Sept. 2020}
  \resumeItemListStart
    \resumeItem{Middleware Development}
      {Developed a middleware using Node.js and AWS Lambda to facilitate data mapping between two service components within the EMIS Clint project. Successfully integrated the solution into the company’s codebase, enhancing system interoperability.}
    \resumeItem{Cost Efficiency Analysis and Optimization}
      {Conducted a comprehensive cost analysis of data storage solutions on AWS RDS, leading to a strategic proposal to migrate to DynamoDB. This initiative reduced costs by 60\% while maintaining performance levels, demonstrating significant savings and operational efficiency.}
    \resumeItem{Cloud Infrastructure Management}
      {Utilized AWS CloudFormation to manage DevOps pipelines and DynamoDB schemas, ensuring robust and scalable cloud infrastructure. Implemented AWS IAM strategies to enhance security through stringent access controls.}
  \resumeItemListEnd

  %-----------EXPERIENCE: Skogame (Java & Gaming)-----------------
  %   \resumeSubheading
  %     {Skogame Ltd.}{Shanghai, China}
  %     {Mobile Gaming Backend Developer}{Jul. 2019 - Sept. 2019}
  %     \resumeItemListStart
  %       \resumeItem{Java Web Server on Netty}
  %           {Develop the logic of the top-up function with its API which allows players can charge money to buy game currency
  %           and Develop other related time-limited top-up activities.}
  %       \resumeItem{Unit \& Integrate Testing}
  %           {Develop a robot-user sample and a Tester app for testing the maximum capacity
  %           and vulnerability of the game server.}
  %       \resumeItem{Databases}
  %           {Maintain the two online servers and inspect both MySQL and Redis databases to ensure the working
  %           performance of the game server.}
  %     \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Fuzz Testing for DPC++}{London, UK}
    {Individual Project Researcher}{Sept. 2021 - Jun. 2022}
    \resumeItemListStart
      \resumeItem{DPC++ Fuzzing Framework}
          {Wrote a dissertation to propose the first fuzzing framework for DPC++ which
          includes an instrument tool to track the coverage and a fuzzer to generate test inputs. Establish a DPC++ code
          collection to benchmark the testing framework effectiveness.}
      \resumeItem{LLVM \& Clang}
          {Implement the testing framework under LLVM compiler infrastructure and use Clang LibTooling API to instrument target program automatically on AST level.}
    \resumeItemListEnd
    \resumeSubheading
    {Ophidia Technologies: Smart Label Project}{London, UK}
    {Tech Team Leader \& Full stack developer}{Jun. 2021 - Dec. 2021}
    \resumeItemListStart
      \resumeItem{Leadership and Architecture Design}
          {Led a team of three software engineers in the design and development of a full stack application for smart e-ink labels. Spearheaded the software architecture planning, ensuring optimal integration of front-end and back-end components for enhanced performance and scalability.}
      \resumeItem{Dockerization and Pipeline}
          {Successfully dockerized the backend API, facilitating smoother, more reliable deployments. Engineered and deployed a CI/CD pipeline on AWS, improving development workflow and deployment efficiency by automating updates and testing processes.}
    \resumeItemListEnd
    % \resumeSubheading
    % {AMEX Challenge Hackathon}{London, UK}
    % {Full Stack Developer}{Best Design Prize}
    % \resumeItemListStart
    %   \resumeItem{Mobile App Developing}
    %       {Use React Native including google map components and redux design to create a mobile app 
    %       for the `ShopSmall' schema for helping both customer and partner shops.}
    %   \resumeItem{Architecture Designing}
    %       {Design and develop the backend API server in Express framework using Node.js and 
    %       add authentication token to API request for data security.}
    % \resumeItemListEnd

    \resumeSubheading
    {AI For The Common Good Hackathon}{London, UK \& Paris, France}
    {Frontend Developer \& Team Leader}{Top 3 Project Prize}
    \resumeItemListStart
      \resumeItem{Project Structure Designing}
          {Make the project brief and MoSCoW list for making a mobile web app for feeding language learning materials based on users' preferences and chatting with other learners.}
      \resumeItem{Frontend UI Developing}
          {Develop the user interface using React.Js and Framework7
          to make a Progressive Web App (PWA) for mobile phones and deploy it on remote web servers.}
    \resumeItemListEnd

    % \resumeSubheading
    % {Visual Mapping App for ANCSSC}{London, UK}
    % {Backend Developer}{Score: 76/100}
    % \resumeItemListStart
    %   \resumeItem{API Provider Developing}
    %       {Use Java Spring Boot to provide APIs for the frontend to obtain the NGOs' project coordinates and 
    %       specific information of the project on Azure Web Server.}
    %   \resumeItem{Server Deployment}
    %       {Use Azure Web Server to deploy the API provider of the tool and initialise the Azure Pipeline to
    %        execute the auto deployment.}
    % \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}